%-------------------------
% Resume in Latex
% Author : Andrii Popesku
% Tailored for: Citco Full Stack Developer
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable (pdflatex only)
\ifdefined\pdfgentounicode
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Andrii Popesku} \\ \vspace{3pt}
    \small Tullamore, Ireland (Open to relocation to Dublin) $|$ \textbf{STAMP 4 VISA HOLDER} \\
    \small \faPhone\ +353 (83) 305 2511 $|$ \faEnvelope\ \href{mailto:uandworker@gmail.com}{uandworker@gmail.com} $|$ 
    \faLinkedin\ \href{https://linkedin.com/in/uand}{linkedin.com/in/uand}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\small{Performance-driven \textbf{Full Stack Developer} with over 2.5 years of experience specializing in \textbf{Python (FastAPI)} and modern \textbf{TypeScript/React} ecosystems. Expert in architecting \textbf{RESTful Web Services} and \textbf{Agentic AI} frameworks (LangChain) within cloud-native environments. Award-winning builder in the \textbf{Fintech space}, recognized for delivering insurance and pension solutions under tight deadlines. Proven ability to implement \textbf{Test-Driven Development (TDD)}, manage automated CI/CD pipelines, and collaborate in service-oriented enterprise architectures.}

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Backend}{: \textbf{Python (Expert)}, \textbf{FastAPI}, Pydantic, REST APIs, Node.js, \textbf{Pytest (TDD)}, Asynchronous Programming.} \\
     \textbf{Frontend}{: \textbf{TypeScript}, \textbf{React 18}, \textbf{Material UI (MUI)}, JavaScript (ES6+), Single-Page Applications (SPA).} \\
     \textbf{AI \& GenAI}{: LangChain, Agentic AI Orchestration, Google ADK, LLMs (GPT-4, Claude), Vector Databases (PGVector).} \\
     \textbf{Cloud \& DevOps}{: \textbf{AWS (ECS, S3, CloudFormation exposure)}, Docker, GCP, Git, GitHub Actions, Jenkins.} \\
     \textbf{Tools}{: Amazon Q, GitHub Copilot, Jira, Bitbucket, Postman, Linux (Terminal-first workflow).}
    }}
 \end{itemize}

%-----------FINANCIAL INDUSTRY EXPERIENCE-----------
\section{Hackathon}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Give(a)Go Hiring Hackathon $|$ \textnormal{\small \textit{Winner -- Kota Challenge}}}{Dublin, Ireland}
      {Lead Full Stack Developer}{March 2026}
      \resumeItemListStart
        \resumeItem{Researched and architected a \textbf{Fintech solution} for Kota's health insurance department in a 4-hour high-pressure sprint.}
        \resumeItem{Developed a React-based SPA featuring a human-in-the-loop AI chatbot and a \textbf{pension/plan calculator}.}
        \resumeItem{Integrated business logic using \textbf{Python and FastAPI}, translating direct insights from Kota’s leadership into a secure, functional prototype.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {shablon.co}{}
      {Founder \& Solo Developer (Full-Stack focus)}{Sept. 2025 -- Present}
      \resumeItemListStart
        \resumeItem{Launched a cloud-based video automation platform utilizing a \textbf{Python (FastAPI)} and \textbf{React 18/MUI} stack.}
        \resumeItem{Implemented \textbf{Agentic workflows} using LangChain to automate multi-step reasoning for content production.}
        \resumeItem{Applied \textbf{TDD best practices} using Pytest to ensure backend resilience for resource-intensive AI compute tasks.}
        \resumeItem{Deployed and managed containerized services via \textbf{Docker} and GCP, maintaining high availability for global users.}
      \resumeItemListEnd

    \resumeSubheading
      {Global Staffing Support}{Chernivtsi, Ukraine}
      {AI Software Engineer}{Aug. 2024 -- Aug. 2025}
      \resumeItemListStart
        \resumeItem{Developed RAG solutions for B2B platforms, improving data retrieval accuracy by 80\% for enterprise clients.}
        \resumeItem{Built and maintained integrations for \textbf{7+ third-party SaaS APIs} (Slack, Drive, etc.) into a service-oriented architecture.}
        \resumeItem{Optimized \textbf{PostgreSQL} vector databases, reducing retrieval latency by 60\% for high-concurrency requests.}
        \resumeItem{Contributed to automated build processes and systems documentation to improve team support efficiencies.}
      \resumeItemListEnd

    \resumeSubheading
      {Global Staffing Support (Intern)}{}
      {AI Software Engineer}{April 2024 -- Aug. 2024}
      \resumeItemListStart
        \resumeItem{Automated unstructured document parsing using \textbf{Python} and NLP pipelines, reducing manual review time by 50\%.}
        \resumeItem{Collaborated with senior leads on debugging and researching alternative technologies for architectural review.}
      \resumeItemListEnd

    \resumeSubheading
      {Freelance}{}
      {Python Automation Developer, Video Editor}{March 2023 -- April 2024}
      \resumeItemListStart
        \resumeItem{Developed custom automation scripts and Restful services for video production products}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Yuriy Fedkovych Chernivtsi National University}{Ukraine}
      {B.S. in Applied Mathematics (STEM / Engineering Equivalent)}{2021 -- 2025}
  \resumeSubHeadingListEnd

\end{document}